Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets

### 2023-12-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure*}
    \script{wg_IVandV_risks.py}
    \begin{centering}
        \includegraphics{figures/wg_IVandV_risks.png}
        \caption{Distributions over the risk for microscopic involvement in \gls{lnl} IV (left panels) and in \gls{lnl} V (right panels) as predicted by the winning graph model, given early (top panels) or advanced T-category (bottom panels), and different CT-based diagnoses: 1) A clinical N0 patient (green histograms), 2) visible metastases in \gls{lnl} II, but otherwise healthy-looking lymph nodes (blue histograms), 3) macroscopic metastases in the \glspl{lnl} II \& III, with the rest of the neck still being clinically node negative (orange histograms), and finally 4) extensive clinical involvement in the levels II, III, and IV (red histograms).\label{fig:wg_IVandV_risks}}
    \end{centering}
\end{figure*}

{\it Level V:} The right panels in \autoref{fig:wg_IVandV_risks} shows the risk of occult disease in level V depending on T-category and the clinical involvement of levels II-IV. For clinically N0 patients, the risk in level V is estimated to be just above 1\%. Extensive nodal involvement of levels II-IV increases the risk in level V to more than 4\% for advanced T-category tumors.

>>>>

\begin{figure*}
    \script{wg_IVandV_risks.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/wg_IVandV_risks.png}
        \caption{Distributions over the risk for microscopic involvement in \gls{lnl} IV (left panels) and in \gls{lnl} V (right panels) as predicted by the winning graph model, given early (top panels) or advanced T-category (bottom panels), and different CT-based diagnoses: 1) A clinical N0 patient (green histograms), 2) visible metastases in \gls{lnl} II, but otherwise healthy-looking lymph nodes (blue histograms), 3) macroscopic metastases in the \glspl{lnl} II \& III, with the rest of the neck still being clinically node negative (orange histograms), and finally 4) extensive clinical involvement in the levels II, III, and IV (red histograms).\label{fig:wg_IVandV_risks}}
    \end{centering}
\end{figure*}

@@

{\it Level V:} The right panels in \autoref{fig:wg_IVandV_risks} show the risk of occult disease in level V depending on T-category and the clinical involvement of levels II-IV. For clinically N0 patients, the risk in level V is estimated to be just above 1\%. Extensive nodal involvement of levels II-IV increases the risk in level V to more than 4\% for advanced T-category tumors.
